---
title: "Alcohol vs Seat choice"
author: "Genevieve Metcalf"
date: "16th September 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

$H_0$ There is no difference in alcohol consumption based on where one sits in class.
$H_A$ There is a difference in alcohol consumption based on where one sits in class.
## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  The boxplot shows that the people who sit in the back tend to consume the most alcohol compared to the people in the front and middle.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```


```{r}
plot(TukeyHSD(model1))
```

The P value is 0.00small so it concludes that we reject the $H_$0; there is a difference on alcohol consumption based on where one sits.

The Tukey test shows that the people in the back consume the most alcohol, the people in the front consume the least, and the middle average out to consuming almost as much as the people in the back.


## Conclusions
In conclusion there is a difference based on the row you sit in for alcohol consumption rate. In this manner it shows the back of the class consumed the most being hidden compared to both the front who can be seen and middle who has a possibility.

